\documentclass{article}
\usepackage[utf8]{inputenc}

\title{DESI fiberassign during survey operations}
\date{March 2020}

\begin{document}

\maketitle

\section{Expected tasks}


The \textbf{Survey Operations} plan includes both Survey Validation
and the 5-year survey.  Following DocDB 3308-v4, Survey Operations
lists four major areas:

\begin{itemize}
    \item Survey management.
    \item Survey validation.
    \item Tracking and reporting
    \item Nightwatch and Exposure Time Calculator
\end{itemize}

Fiberassign is explicitly included under  \textbf{Survey Management}
with the following tasks:

\begin{enumerate}
\item Run the fiberassign code to provide assignments of fibers to
  input targets, stars (calibration and guide/focus arrays) and sky
  locations. 

\item Track the number of exposures for each LRG target for
  reaching a number pre-determined by each galaxy’s magnitude. 

\item Re-observe the high-redshift QSO targets if they are
  determined to be a high-confidence target from previous observations.

\item Ensure the reproducibility of fiber assignment for the
  selection functions of the Large Scale Structure catalogs.

\item Implement modifications necessary for failures of individual
  fibers or other constraints imposed by changes to the instrument
  during operations. 
\end{enumerate}

\section{Current Status}

\begin{itemize}
\item During Survey Validation (SV0, March 2020) Task 1 was routinely performed (Sarah).

\item There is end-to-end simulation work to start tackling Task 2 (Jaime).

\item There is work in progress with the Lya QSO working group to explore and implement changes that address Task 3 (Jaime).

\item First successful attempts to address Task 4 have been already performed on simulations (1\% survey) and SV0 data (Ashley). 

\item Task 5 was continuously performed during commissioning and SV0 (Ted). 
\end{itemize}
 
\section{Questions}

\begin{enumerate}
\item What is the expected cadence to update the Merged Target List
  (MTL) with spectroscopic information and run fiberassign? (As per
  DESI-3308 one week cadence is expected from the Lyman-Alpha Decision
  Lead.) 
\item What is the actual plan to update and freeze a new MTL that
  will be fed to fiberassign?
\item There are 29 open issues on the fiberassign repo (March 31,
  2020). What are their relative priorities?
\end{enumerate}

\end{document}
